---
title: "CUPN_Mapping_Tree"
output: html_document
date: '2023-01-20'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Map 2: Tree Regeneration By Size Class
Map 5: Regeneration Composition
Map 6: Canopy Composition
Map 8: Priority Invasive Composition
Map 8b: Not done by NETN, but agreed that we'd all like a map of relative abundance of Native versus Exotic by plot.  Should be very straigtforward, two colors (one for native, one for exotic)

```{r}
library(tidyverse) 
library(dplyr)
library(httr)
library(rgdal) 
library(sf) 
library(RColorBrewer)
library(sp) 
library(rgeos)
library(leaflet)
library(leaflet.minicharts)
library(mapview)
library(lubridate)


#setwd("C:/Users/kseeger/OneDrive - DOI/Desktop/GIT_RSTUDIO/SER_VEG_Team)
tree_basics <- read_csv(here::here("DataIn","TreeBasics_20221013.csv"))
seed_sap <- read_csv(here::here("DataIn","SeedlingSapling_20221013.csv"))
#seed_sap has become only CARL plots in this script

```

#Seedling and Sapling data for CUPN CARL Plots 
```{r}
seed_sap <- seed_sap %>%
dplyr::filter(grepl("CARL", Plot_Code)) %>%
dplyr::filter(Event_Type_Name != "QA/QC")

```

#CUPN Plot Lat and Long
```{r}
cupn_plots <- read_csv(here::here("DataIn","CUPN_PlotEvents_LatLong.csv"))

cupn_plots_select <- cupn_plots %>%
    dplyr::select(Plot_Code, Start_Date, Latitude, Longitude)

cupn_plots_select$Start_Date <- dmy(cupn_plots_select$Start_Date)

cupn_plots_select <- cupn_plots_select %>%
  group_by(Plot_Code) %>%
  slice(which.max(Start_Date))

cupn_carl <- cupn_plots_select %>%
    dplyr::filter(grepl("CARL", Plot_Code)) %>%
  dplyr::select(-Start_Date)

```

#adding CUPN shapefiles 
```{r}
cupn_boundary <- st_read(here::here('./cupnshapefile/CUPN.shp'))

st_crs(cupn_boundary)

```

#creating color palettes
```{r}
okabe_ito <- c( "#0072B2", "#D55E00", 
               "#CC79A7", "#000000",  '#CC6677', '#BBCC33', '#99DDFF', 
                '#332288', '#882255', '#FFAABB', "#E69F00", "#56B4E9", "#009E73", "#F0E442")

viridis <- c("#fde725", "#5ec962", "#21918c","#3b528b","#440154")

```

#selecting top 13 species present in seedling/saplings and tree species
#TRY USING FORCATS() PACKAGE: FCT_LUMP()

```{r}
#Seedling Sapling

# trying code to see if fct_lump would be a better alternative
# lword <- seed_sap %>%
# filter(!is.na(Plant_Code)) %>%
# mutate(Plant_Code = fct_lump(Plant_Code, n = 10)) %>%
# count(Plant_Code)

top_species <- seed_sap %>%
dplyr::mutate(Plant_Code = as.factor(Plant_Code)) %>%
  group_by(Plant_Code) %>%
  summarise(Observations = n()) %>%
  arrange(desc(Observations))  %>%
dplyr::mutate(Plant_Code = as.character(Plant_Code))

top_species <- as.data.frame(top_species[top_species$Observations >20,])

tree_basics_count <- tree_basics %>%
dplyr::filter(Park_Code == "CARL")%>%
  dplyr::filter(Event_Type_Name != "QA/QC") %>%
dplyr::filter(Status_Code == 1) %>%
  dplyr::mutate(Basal_Area_ha = ((pi * DBH^2) /40000 )/0.04)

#Tree
top_tree <- tree_basics_count %>%
dplyr::mutate(Plant_Code = as.factor(Plant_Code)) %>%
  group_by(Plant_Code) %>%
  summarise(Observations = n()) %>%
  arrange(desc(Observations))  %>%
dplyr::mutate(Plant_Code = as.character(Plant_Code))

top_tree <- as.data.frame(top_tree[top_tree$Observations >20,])
```

#creating list of most frequently occuring tree species
```{r}
species_col_palette <- rbind(top_tree, top_species)

species_col_palette <- species_col_palette %>%
  dplyr::select(Plant_Code) %>%
  dplyr::mutate(Plant_Code = as.factor(Plant_Code))

species_col_palette <- unique(species_col_palette)

tree_count_test <- tree_basics_count %>%
dplyr::filter(Plant_Code %in% species_col_palette$Plant_Code)

unique(tree_count_test$Plant_Code)
```

#creating "Other category" in tree species count
```{r}
tree_basics_test_other <- tree_basics_count %>%
dplyr::filter(!Plant_Code %in% species_col_palette$Plant_Code)

tree_basics_test_other <- tree_basics_test_other %>%
  group_by(Plot_Code) %>%
  summarize(Other = n())
```

#creating tree_count: # basal area, # other, # obs per species
```{r}
#count number of observations of trees for tree density
tree_count_test <- tree_count_test %>%
  group_by(Plot_Code, Plant_Code) %>%
  summarize(DBH_Obs = n()) %>%
  ungroup()

tree_count_test <- tree_count_test %>%
  pivot_wider(names_from = Plant_Code, 
              values_from = DBH_Obs)

tree_count_test <- tree_count_test[,c(names(tree_count_test)[1],sort(names(tree_count_test)[2:14]))]

tree_ba_test<- tree_basics_count %>%
  group_by(Plot_Code) %>%
  summarise(Sum = sum(Basal_Area_ha))

tree_plot_test <-  Reduce(function (...) { merge(..., all = TRUE) },  # Full join
                           list(tree_ba_test, tree_basics_test_other, tree_count_test, cupn_carl))

```
#mapping subsetted TREE data
```{r}
baseman_carl = leaflet(data = tree_plot_test) %>%
  addTiles() %>%
  #addProviderTiles("Esri.WorldImagery", options = providerTileOptions(noWrap = TRUE), group="Satellite") %>%
  addPolygons(data = cupn_boundary, color = ~ "black") %>%
  addCircleMarkers(tree_plot_test$Longitude,
                   tree_plot_test$Latitude,  color = ~ "black", weight = 1, fillColor = ~"blue", fillOpacity = 1, radius = 4)

#SET VIEW SETS THE MIDDLE POINT OF THE MAP BUT DOES NOT NECESARRILY HELP FOR VIEWING PURPOSES
#  setView(lng = mean(tree_plot_test$Longitude), lat = mean(tree_plot_test$Latitude), zoom = 15)

baseman_carl <- baseman_carl %>%
  addMinicharts(tree_plot_test$Longitude, 
                tree_plot_test$Latitude, 
    chartdata =dplyr::select(tree_plot_test, Other:SASSALB), 
    type = "pie",
    width = sqrt(tree_plot_test$Sum) * 4,
    col = okabe_ito,
    showLabels = F) %>%
  addLabelOnlyMarkers(tree_plot_test$Longitude, 
                tree_plot_test$Latitude, label =  tree_plot_test$Plot_Code,
                      labelOptions = labelOptions(noHide = T, direction = 'top', textOnly = T, style=list('color'="#ffffff", 'fontSize'="15px"))) %>%
      fitBounds(min(tree_plot_test$Longitude), min(tree_plot_test$Latitude), max(tree_plot_test$Longitude), max(tree_plot_test$Latitude))

baseman_carl
mapshot(baseman_carl, file = "Map_TreeCanopy_Comp.png")
```

#SEEDLING SAPLING regeneration composition
```{r}
seed_sap_test <- seed_sap %>%
dplyr::filter(Plant_Code %in% species_col_palette$Plant_Code)

seed_sap_test <- seed_sap_test %>%
  replace(is.na(.), 0)
```

#Counting occurance of top seedling/sapling species 

```{r}
seed_sap_test <- seed_sap_test %>%
  dplyr::select(Plot_Code, Plant_Code, Seedling_5_15_Tall:Sapling_5_10_DBH) %>%
  group_by(Plot_Code, Plant_Code) %>%
  summarize(across(where(is.numeric), ~sum(.x, na.rm = TRUE))) %>%
  ungroup()

seed_sap_test <- seed_sap_test %>%
  dplyr::mutate(Count = rowSums(across(where(is.numeric)))) %>%
  dplyr::select(Plot_Code, Plant_Code, Count)

seed_sap_test <- seed_sap_test %>%
  pivot_wider(values_from = Count, 
              names_from = Plant_Code)

seed_sap_test <- seed_sap_test[,c(names(seed_sap_test)[1],sort(names(seed_sap_test)[2:14]))]

seed_sap_test <- seed_sap_test %>%
  dplyr::mutate(sum = rowSums(across(where(is.numeric)), na.rm= TRUE))
  
```
#Creating other variable for less prevalent species
```{r}
seed_sap_other_test <- seed_sap %>%
dplyr::filter(!Plant_Code %in% species_col_palette$Plant_Code)

seed_sap_other_test <- seed_sap_other_test %>%
  replace(is.na(.), 0)

seed_sap_other_test <- seed_sap_other_test %>%
dplyr::mutate(SapCount = rowSums(across(Seedling_15_30_Tall:Sapling_5_10_DBH)))

seed_sap_other_test <- seed_sap_other_test %>%
  dplyr::select(Plot_Code, SapCount) %>%
  group_by(Plot_Code) %>%
  summarize(Other = sum(SapCount))
  
```

#Calculating stem densities per hectare
```{r}
seed_sap_den_test <- seed_sap %>%
  dplyr::mutate(
    Seedling_Den_15_30_Tall = Seedling_15_30_Tall/0.0008,
    Seedling_Den_30_50_Tall = Seedling_30_50_Tall/0.0008,
    Seedling_Den_50_137_Tall = Seedling_50_137_Tall/0.0008,
    Sapling_Den_0_1_DBH = Sapling_0_1_DBH/0.008, 
    Sapling_Den_1_2half_DBH = Sapling_1_2half_DBH/0.008,
    Sapling_Den_2half_5_DBH = Sapling_2half_5_DBH/0.008,
    Sapling_Den_5_10_DBH = Sapling_5_10_DBH/0.008
  )

seed_sap_den_test <- seed_sap_den_test %>%
 dplyr::select(Plot_Code, Plant_Code, Seedling_Den_15_30_Tall, Seedling_Den_30_50_Tall, Seedling_Den_50_137_Tall, Sapling_Den_0_1_DBH, Sapling_Den_1_2half_DBH, Sapling_Den_2half_5_DBH, Sapling_Den_5_10_DBH)%>%
  replace(is.na(.), 0) %>%
  group_by(Plot_Code) %>%
  summarize(across(where(is.numeric), ~sum(.x, na.rm = TRUE))) %>%
  ungroup()
  

seed_sap_den_test <- seed_sap_den_test %>%
  group_by(Plot_Code) %>%
dplyr::mutate(seed_sap_density = sum(Seedling_Den_15_30_Tall,
                                Seedling_Den_30_50_Tall,
                                Seedling_Den_50_137_Tall,Sapling_Den_0_1_DBH, 
                               Sapling_Den_1_2half_DBH,
                               Sapling_Den_2half_5_DBH, 
                               Sapling_Den_5_10_DBH)) %>%
  ungroup()

seed_sap_den_test <- seed_sap_den_test %>%
 dplyr::select(Plot_Code, seed_sap_density)

seed_sap_test <- Reduce(function (...) { merge(..., all = TRUE) },  # Full join
                           list( seed_sap_other_test, seed_sap_test, seed_sap_den_test, cupn_carl))

```

#Mapping Seedling/Sapling Regeneration by Composition
```{r}
baseman_carl = leaflet(data = seed_sap_test) %>%
  addProviderTiles("Esri.WorldImagery", options = providerTileOptions(noWrap = TRUE), group="Satellite") %>%
  addPolygons(data = cupn_boundary, color = ~ "black") %>%
  addCircleMarkers(seed_sap_test$Longitude,
                   seed_sap_test$Latitude,  color = ~ "black", weight = 1, fillColor = ~"blue", fillOpacity = 1, radius = 4)

#SET VIEW SETS THE MIDDLE POINT OF THE MAP BUT DOES NOT NECESARRILY HELP FOR VIEWING PURPOSES
#  setView(lng = mean(seed_sap_top$Longitude), lat = mean(seed_sap_top$Latitude), zoom = 15)

baseman_carl <- baseman_carl %>%
  setView(lng = mean(seed_sap_test$Longitude), lat = mean(seed_sap_test$Latitude), zoom = 16) %>%
  addMinicharts(seed_sap_test$Longitude, 
                seed_sap_test$Latitude, 
    chartdata = dplyr::select(seed_sap_test, Other:SASSALB), 
    type = "pie",
    width = sqrt(seed_sap_test$seed_sap_density)/6.5,
    col = okabe_ito,
    showLabels = F) %>%
  addLabelOnlyMarkers(seed_sap_test$Longitude, 
                seed_sap_test$Latitude, label =  seed_sap_test$Plot_Code,
                      labelOptions = labelOptions(noHide = T, direction = 'top', textOnly = T, style=list('color'="#ffffff", 'fontSize'="15px"))) #SEEING IF YOU CAN MAPSHOT THE CURRENT SUBSETTED VIEW 

#%>%
     # fitBounds(min(seed_sap_test$Longitude), min(seed_sap_test$Latitude), max(seed_sap_test$Longitude), max(seed_sap_test$Latitude))


baseman_carl

# mapshot(baseman_carl, file = "Leaflet_CARLMap5_Ttest.png")

```

#SEPARATING SEEDLINGS AND SAPLINGS 
#SEEDLING regeneration composition
```{r}
seed_test <- seed_sap %>%
dplyr::filter(Plant_Code %in% species_col_palette$Plant_Code)

seed_test <- seed_test %>%
  replace(is.na(.), 0)
```

#Counting occurance of top species 
```{r}
seed_test <- seed_test %>%
 dplyr::select(Plot_Code, Plant_Code, Seedling_5_15_Tall:Seedling_50_137_Tall) %>%
  group_by(Plot_Code, Plant_Code) %>%
  summarize(across(where(is.numeric), ~sum(.x, na.rm = TRUE))) %>%
  ungroup()

seed_test <- seed_test %>%
dplyr::mutate(Count = rowSums(across(where(is.numeric)))) %>%
 dplyr::select(Plot_Code, Plant_Code, Count)

seed_test <- seed_test %>%
  pivot_wider(values_from = Count, 
              names_from = Plant_Code)

seed_test <- seed_test[,c(names(seed_test)[1],sort(names(seed_test)[2:14]))]

seed_test <- seed_test %>%
dplyr::mutate(sum = rowSums(across(where(is.numeric)), na.rm= TRUE))
  
```
#Creating other variable for less prevalent species
```{r}
seed_other_test <- seed_sap %>%
dplyr::filter(!Plant_Code %in% species_col_palette$Plant_Code)

seed_other_test <- seed_other_test %>%
  replace(is.na(.), 0)

seed_other_test <- seed_other_test %>%
dplyr::mutate(SeedCount = rowSums(across(Seedling_15_30_Tall:Seedling_50_137_Tall)))

seed_other_test <- seed_other_test %>%
  dplyr::select(Plot_Code, SeedCount) %>%
  group_by(Plot_Code) %>%
  summarize(Other = sum(SeedCount))
  
```

#Calculating stem densities per hectare
```{r}
seed_den_test <- seed_sap %>%
  dplyr::mutate(
    Seedling_Den_15_30_Tall = Seedling_15_30_Tall/0.0008,
    Seedling_Den_30_50_Tall = Seedling_30_50_Tall/0.0008,
    Seedling_Den_50_137_Tall = Seedling_50_137_Tall/0.0008
  )

seed_den_test <- seed_den_test %>%
 dplyr::select(Plot_Code, Plant_Code, Seedling_Den_15_30_Tall, Seedling_Den_30_50_Tall, Seedling_Den_50_137_Tall )%>%
  replace(is.na(.), 0) %>%
  group_by(Plot_Code) %>%
  summarize(across(where(is.numeric), ~sum(.x, na.rm = TRUE))) %>%
  ungroup()
  

seed_den_test <- seed_den_test %>%
  group_by(Plot_Code) %>%
dplyr::mutate(seed_density = sum(Seedling_Den_15_30_Tall,
                                Seedling_Den_30_50_Tall,
                                Seedling_Den_50_137_Tall
                               )) %>%
  ungroup()

seed_den_test <- seed_den_test %>%
 dplyr::select(Plot_Code, seed_density)

seed_test <- Reduce(function (...) { merge(..., all = TRUE) },  # Full join
                           list( seed_other_test, seed_test, seed_den_test, cupn_carl))

```

```{r}
baseman_carl = leaflet(data = seed_test) %>%
  addTiles() %>%
  addPolygons(data = cupn_boundary, color = ~ "black", fillColor = ~"white", fillOpacity = 0.6) %>%
  addCircleMarkers(seed_test$Longitude,
                   seed_test$Latitude,  color = ~ "black", weight = 1, fillColor = ~"blue", fillOpacity = 1, radius = 4)

#SET VIEW SETS THE MIDDLE POINT OF THE MAP BUT DOES NOT NECESARRILY HELP FOR VIEWING PURPOSES
#  setView(lng = mean(seed_sap_top$Longitude), lat = mean(seed_sap_top$Latitude), zoom = 15)

baseman_carl <- baseman_carl %>%
  setView(lng = mean(seed_test$Longitude), lat = mean(seed_test$Latitude), zoom = 16) %>%
  addMinicharts(seed_test$Longitude, 
                seed_test$Latitude, 
    chartdata = dplyr::select(seed_test, Other:SASSALB), 
    type = "pie",
    width = sqrt(seed_test$seed_density)/6.5,
    col = okabe_ito,
    showLabels = F) %>%
  addLabelOnlyMarkers(seed_test$Longitude, 
                seed_test$Latitude, label =  seed_test$Plot_Code,
                      labelOptions = labelOptions(noHide = T, direction = 'top', textOnly = T, style=list('color'="#000000", 'fontSize'="15px"))) %>%
      fitBounds(min(seed_test$Longitude), min(seed_test$Latitude), max(seed_test$Longitude), max(seed_test$Latitude))


baseman_carl
#mapshot(baseman_carl, file = "Map_SeedlingSpecies_Comp.png")

```

#MAP 5 TESTINGGGGNGNGNGNG SAPLING regeneration composition
```{r}
sap_test <- seed_sap %>%
dplyr::filter(Plant_Code %in% species_col_palette$Plant_Code)

sap_test <- sap_test %>%
  replace(is.na(.), 0)
```

#Counting occurance of top sapling species 
```{r}
sap_test <- sap_test %>%
 dplyr::select(Plot_Code, Plant_Code, Sapling_0_1_DBH:Sapling_5_10_DBH) %>%
  group_by(Plot_Code, Plant_Code) %>%
  summarize(across(where(is.numeric), ~sum(.x, na.rm = TRUE))) %>%
  ungroup()

sap_test <- sap_test %>%
dplyr::mutate(Count = rowSums(across(where(is.numeric)))) %>%
 dplyr::select(Plot_Code, Plant_Code, Count)

sap_test <- sap_test %>%
  pivot_wider(values_from = Count, 
              names_from = Plant_Code)

sap_test <- sap_test[,c(names(sap_test)[1],sort(names(sap_test)[2:14]))]

sap_test <- sap_test %>%
dplyr::mutate(sum = rowSums(across(where(is.numeric)), na.rm= TRUE))
  
```
#Creating other variable for less prevalent species
```{r}
sap_other_test <- seed_sap %>%
dplyr::filter(!Plant_Code %in% species_col_palette$Plant_Code)

sap_other_test <- sap_other_test %>%
  replace(is.na(.), 0)

sap_other_test <- sap_other_test %>%
dplyr::mutate(SapCount = rowSums(across(Sapling_0_1_DBH:Sapling_5_10_DBH)))

sap_other_test <- sap_other_test %>%
  dplyr::select(Plot_Code, SapCount) %>%
  group_by(Plot_Code) %>%
  summarize(Other = sum(SapCount))
  
```

#Calculating stem densities per hectare
```{r}
sap_den_test <- seed_sap %>%
  dplyr::mutate(
    Sapling_Den_0_1_DBH = Sapling_0_1_DBH/0.008,
    Sapling_Den_1_2half_DBH = Sapling_1_2half_DBH/0.008,
    Sapling_Den_2half_5_DBH = Sapling_2half_5_DBH/0.008,
    Sapling_Den_5_10_DBH = Sapling_5_10_DBH/0.008
  )

sap_den_test <- sap_den_test %>%
 dplyr::select(Plot_Code, Plant_Code,
               Sapling_Den_0_1_DBH, Sapling_Den_1_2half_DBH, Sapling_Den_2half_5_DBH, Sapling_Den_5_10_DBH
               )%>%
  replace(is.na(.), 0) %>%
  group_by(Plot_Code) %>%
  summarize(across(where(is.numeric), ~sum(.x, na.rm = TRUE))) %>%
  ungroup()
  

sap_den_test <- sap_den_test %>%
  group_by(Plot_Code) %>%
dplyr::mutate(sap_density = sum(Sapling_Den_0_1_DBH, 
                               Sapling_Den_1_2half_DBH,
                               Sapling_Den_2half_5_DBH,
                               Sapling_Den_5_10_DBH
                               )) %>%
  ungroup()

sap_den_test <- sap_den_test %>%
 dplyr::select(Plot_Code, sap_density)

sap_test <- Reduce(function (...) { merge(..., all = TRUE) },  # Full join
                           list( sap_other_test, sap_test, sap_den_test, cupn_carl))
```

```{r}
baseman_carl = leaflet(data = sap_test) %>%
  addTiles() %>%
  addPolygons(data = cupn_boundary, color = ~ "black") %>%
  addCircleMarkers(sap_test$Longitude,
                   sap_test$Latitude,  color = ~ "black", weight = 1, fillColor = ~"blue", fillOpacity = 1, radius = 4)

#SET VIEW SETS THE MIDDLE POINT OF THE MAP BUT DOES NOT NECESARRILY HELP FOR VIEWING PURPOSES
#  setView(lng = mean(seed_sap_top$Longitude), lat = mean(seed_sap_top$Latitude), zoom = 15)

baseman_carl <- baseman_carl %>%
  setView(lng = mean(sap_test$Longitude), lat = mean(sap_test$Latitude), zoom = 16) %>%
  addMinicharts(sap_test$Longitude, 
                sap_test$Latitude, 
    chartdata = dplyr::select(sap_test, Other:SASSALB), 
    type = "pie",
    width = sqrt(sap_test$sap_density)/2.75, #this is different from the seedling map
    col = okabe_ito,
    showLabels = F) %>%
  addLabelOnlyMarkers(sap_test$Longitude, 
                sap_test$Latitude, label =  sap_test$Plot_Code,
                      labelOptions = labelOptions(noHide = T, direction = 'top', textOnly = T, style=list('color'="#000000", 'fontSize'="15px")))%>% #SEEING IF YOU CAN MAPSHOT THE CURRENT SUBSETTED VIEW 


    fitBounds(min(sap_test$Longitude), min(sap_test$Latitude), max(sap_test$Longitude), max(sap_test$Latitude))


baseman_carl
```

```{r}
species_rich <- read_csv("SpeciesDiversity_LongFormat.csv")

sp_native_prop <- species_rich %>%
  dplyr::filter(Event_Type != "QA/QC") %>%
  dplyr::filter(grepl("CARL", Plot_Code)) %>%
  group_by(Plot_Code, Nativity) %>%
  summarize(sum = n()) %>%
  ungroup()
  

sp_native_prop <- sp_native_prop %>%
  pivot_wider(names_from = Nativity, 
              values_from = sum)
sp_native_prop <- sp_native_prop %>%
  rename(Other = `NA`)

carl_nativity <- left_join(sp_native_prop, cupn_carl, by = "Plot_Code")

```

```{r}
baseman_carl = leaflet(data = carl_nativity) %>%
  addTiles() %>%
  addPolygons(data = cupn_boundary, color = ~ "black") %>%
  addCircleMarkers(carl_nativity$Longitude,
                   carl_nativity$Latitude,  color = ~ "black", weight = 1, fillColor = ~"blue", fillOpacity = 1, radius = 4)

baseman_carl <- baseman_carl %>%
 # setView(lng = mean(carl_nativity$Longitude), lat = mean(carl_nativity$Latitude), zoom = 16) %>%
  addMinicharts(carl_nativity$Longitude, 
                carl_nativity$Latitude, 
    chartdata = dplyr::select(carl_nativity, Native:Other), 
    type = "pie",
 #this is different from the seedling map
    col = okabe_ito,
    showLabels = F) %>%
  addLabelOnlyMarkers(carl_nativity$Longitude, 
                carl_nativity$Latitude, label =  carl_nativity$Plot_Code,
                      labelOptions = labelOptions(noHide = T, direction = 'top', textOnly = T, style=list('color'="#000000", 'fontSize'="15px")))%>% #SEEING IF YOU CAN MAPSHOT THE CURRENT SUBSETTED VIEW 


    fitBounds(min(carl_nativity$Longitude), min(carl_nativity$Latitude), max(carl_nativity$Longitude), max(carl_nativity$Latitude))


baseman_carl
```

