---
title: "SECN_Mapping_Constancy"
output: html_document
date: '2023-01-05'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
###I THINK THAT CONSTAnCY IS A BAD VARIABLE TO GRAPH BECAUSE IT IS FREQUENCY OF SPECIES OVER SPECIFIC AREA, TOO MANY SPECIES TO SHOW PER PLOT

Map 2: Tree Regeneration By Size Class
Map 5: Regeneration Composition
Map 6: Canopy Composition
Map 8: Priority Invasive Composition
Map 8b: Not done by NETN, but agreed that we'd all like a map of relative abundance of Native versus Exotic by plot.  Should be very straightforward, two colors (one for native, one for exotic)

```{r}
library(ggplot2)
library(readr)
library(knitr)
library(base)
library(stringr)
library(gt)
library(psych)
library(tidyverse) 
library(dplyr)
library(httr)
library(rgdal) 
library(sf) 
library(RColorBrewer)
library(sp) 
library(rgeos)
library(leaflet)
library(leaflet.minicharts)
library(mapview)
```

```{r}
#Set Working Directory
setwd("C:/Users/kseeger/OneDrive - DOI/Desktop/GIT_RSTUDIO/FlexdashboardPractice/Mapping/SECN")
constancy <- read_csv("Constancy_Data.csv")
constancy_full <- read_csv("Constancy_Data_Full.csv")
```

```{r}
#OKABE PALETTE

okabe_ito <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", 
               "#CC79A7", "#000000",  '#CC6677','#DDDDDD', '#EE6677', '#99DDFF', 
               '#BBCC33', '#332288', '#882255', '#FFAABB')
# 
# color_pallete_function <- colorRampPalette(
#   colors = Okabe_Ito, 
#   space = "Lab")
# 
# num_colors <- nlevels(BISCCHH_SP_Rich$Species)
# okabepalette <- color_pallete_function(num_colors)
# okabepalette <- setNames(okabepalette, levels(BISCCHH_SP_Rich$Species))

```

```{r}
# BISCMAN PLOTS
TIMUboundary <- st_read('./SECN_SamplingFrame/TIMU/TIMU_TR_SampleFrame_Jan2020.shp')

st_crs(TIMUboundary)

plot(TIMUboundary)
```

#importing CARL Shapefile
```{r}
park_code <- "TIMU"
  # KATE, ENTER 4-LETTER PARK CODE HERE
  
unitBoundaryURL_TIMU<- paste0("https://services1.arcgis.com/fBc8EJBxQRMcHlei/ArcGIS/rest/services/IMD_Units_Generic_areas_of_analysis_(AOAs)_-_IMD_BND_ALL_UNITS_AOA_nad_py_view/FeatureServer/0/query?where=UNITCODE+%3D+%27", park_code, "%27&objectIds=&time=&geometry=&geometryType=esriGeometryEnvelope&inSR=&spatialRel=esriSpatialRelIntersects&distance=&units=esriSRUnit_Meter&relationParam=&outFields=*&returnGeometry=true&maxAllowableOffset=&geometryPrecision=&outSR=4326&gdbVersion=&returnDistinctValues=false&returnIdsOnly=false&returnCountOnly=false&returnExtentOnly=false&orderByFields=&groupByFieldsForStatistics=&outStatistics=&returnZ=false&returnM=false&resultOffset=&resultRecordCount=&f=geojson") # save output as WGS84

#paste(unitBoundaryURL)
```

```{r}
#checking error code below
imported_dat_TIMU <- tryCatch(readOGR(dsn = unitBoundaryURL_TIMU, dropNULLGeometries = FALSE), error=function(e) print("Error retrieving data")) # return error message if problems still arise with downloading from web services

#shiny::req(class(imported_dat)=="SpatialPolygonsDataFrame")
imported_dat_TIMU <- sp::spTransform(imported_dat_TIMU, CRS("+proj=longlat +datum=WGS84")) # convert to WGS84

plot(imported_dat_TIMU)
```




#Altering Constancy_Full dataset 
```{r}
constancy_full <- constancy_full%>%
  separate(event_name_date_calc, c("Plot_Code", "Date"))

constancy_full

constancy_calc <- constancy_full %>%
  dplyr::select(Plot_Code, 
                Species_Original,
                `Mean Plot Cover`) %>%
  group_by(Plot_Code,
           Species_Original) %>%
  summarise(Avg_MPC = mean(`Mean Plot Cover`)) 
```

#Finding the total number of species in each of the broadly defined habitats
```{r}


constancy_full %>%
  dplyr::select(`BROAD HABITAT TYPE`, Plot_Code) %>%
  group_by(`BROAD HABITAT TYPE`) %>%
  summarize(count_dis = n_distinct(Plot_Code))
```

#Calculating constancy
```{r}
Constancy_Count <- Constancy_Full %>%
  dplyr::select(`BROAD HABITAT TYPE`, Species_Original, `Mean Plot Cover`) %>%
  group_by(`BROAD HABITAT TYPE`, Species_Original) %>%
  summarise(Species_Total = n()) 
```


```{r}
#Finding Average Mean Plot Cover by Species across broad habitat types
Constancy_Calc <- Constancy_Full %>%
  dplyr::select(`BROAD HABITAT TYPE`, 
                Species_Original,
                `Mean Plot Cover`) %>%
  group_by(`BROAD HABITAT TYPE`,
           Species_Original) %>%
  summarise(Avg_MPC = mean(`Mean Plot Cover`)) 

#Pivoting
Constancy_Calc <- Constancy_Calc %>%
  pivot_wider(
    names_from = `BROAD HABITAT TYPE`, 
    values_from = Avg_MPC
  )

Constancy_Calc <- Constancy_Calc %>%
  rename(CPNW = `Coastal Plain Nonalluvial Wetlands`, 
         CPOUW = `Coastal Plain Open Uplands and Woodlands`, 
         MUFS = `Maritime Upland Forests and Shrublands`)

```

```{r}
#Calculating Cover Code
#Is it worth it to figure out for loops???

Cover_Calc <- Constancy_Calc %>%
  dplyr::mutate(CPNW_Cover = case_when(
    CPNW == NA ~ "",
    CPNW >= 0 & CPNW <=0.1~ "1", 
    CPNW >= 0.1 & CPNW <=1~ "2",
    CPNW >= 1 & CPNW <= 2 ~ "3",
    CPNW >= 2 & CPNW <= 5 ~ "4",
    CPNW >= 5 & CPNW <= 10 ~ "5",
    CPNW >= 10 & CPNW <=25~ "6",
    CPNW >= 25 & CPNW <=50~ "7",
    CPNW >= 50 & CPNW <= 75 ~ "8",
    CPNW >= 75 & CPNW <=95 ~ "9",
    CPNW >= 95 & CPNW <= 100 ~ "10"),
CPOUW_Cover = case_when(CPOUW == NA ~ "",
    CPOUW >= 0 & CPOUW <=0.1~ "1", 
    CPOUW >= 0.1 & CPOUW <=1~ "2",
    CPOUW >= 1 & CPOUW <= 2 ~ "3",
    CPOUW >= 2 & CPOUW <= 5 ~ "4",
    CPOUW >= 5 & CPOUW <= 10 ~ "5",
    CPOUW >= 10 & CPOUW <=25~ "6",
    CPOUW >= 25 & CPOUW <=50~ "7",
    CPOUW >= 50 & CPOUW <= 75 ~ "8",
    CPOUW >= 75 & CPOUW <=95 ~ "9",
    CPOUW >= 95 & CPOUW <= 100 ~ "10"),
MUFS_Cover = case_when(MUFS == NA ~ "",
                     MUFS >= 0 & MUFS <=0.1~ "1",
                     MUFS >= 0.1 & MUFS <=1~ "2",
                     MUFS >= 1 & MUFS <= 2 ~ "3",
                     MUFS >= 2 & MUFS <= 5 ~ "4",
                     MUFS >= 5 & MUFS <= 10 ~ "5",
                     MUFS >= 10 & MUFS <=25~ "6",
                     MUFS >= 25 & MUFS <=50~ "7",
                     MUFS >= 50 & MUFS <= 75 ~ "8",
                     MUFS >= 75 & MUFS <=95 ~ "9",
                     MUFS >= 95 & MUFS <= 100 ~ "10")
    
  )
```


```{r}
#Cover Calculations 
Cover_Calc <- Cover_Calc %>%
  dplyr::mutate(CPNW_Cover = as.numeric(CPNW_Cover), 
         CPOUW_Cover = as.numeric(CPOUW_Cover), 
         MUFS_Cover = as.numeric(MUFS_Cover))
```

```{r}
#Finding count of "event_name_date_calc" /species? across broad habitat types 
#

Constancy_Count <- Constancy_Full %>%
  dplyr::select(`BROAD HABITAT TYPE`, Species_Original, `Mean Plot Cover`) %>%
  group_by(`BROAD HABITAT TYPE`, Species_Original) %>%
  summarise(Species_Total = n()) 

Constancy_Count <- Constancy_Count %>%
  pivot_wider(
    names_from = `BROAD HABITAT TYPE`, 
    values_from = Species_Total
  )

```

```{r}
#Calculating Constancy values 
Constancy_Count <- Constancy_Count %>%
  replace(is.na(.), 0) %>%
  dplyr::mutate(
    CPNW_Constancy = ((`Coastal Plain Nonalluvial Wetlands`/max(`Coastal Plain Nonalluvial Wetlands`)) * 100),
    CPOUW_Constancy = ((`Coastal Plain Open Uplands and Woodlands`/max(`Coastal Plain Open Uplands and Woodlands`)) * 100), 
    MUFS_Constancy = ((`Maritime Upland Forests and Shrublands`/max(`Maritime Upland Forests and Shrublands`))*100 )
  )


round_df <- function(x, digits) {
    numeric_columns <- sapply(x, mode) == 'numeric'
    x[numeric_columns] <-  round(x[numeric_columns], digits)
    x
}

Constancy_Count <- round_df(Constancy_Count, 0)

```

```{r}
Cover_Calc_Code <- Cover_Calc %>%
  dplyr::select(Species_Original, CPNW_Cover, CPOUW_Cover, MUFS_Cover) 

Constancy_Count_Code <- Constancy_Count %>%
  dplyr::select(Species_Original, CPNW_Constancy, CPOUW_Constancy, MUFS_Constancy) 
```

```{r}
Constancy_Final <- Reduce(function (...) { merge(..., all = TRUE) },  # Full join
                           list(Cover_Calc_Code, Constancy_Count_Code))
```


```{r}

Constancy_Final <- Constancy_Final %>%
  dplyr::select(Species_Original, CPNW_Constancy, CPNW_Cover, CPOUW_Constancy, CPOUW_Cover, MUFS_Constancy, MUFS_Cover)
```

```{r}
Constancy_Final[Constancy_Final == 0] <- NA

Constancy_Final[is.na(Constancy_Final)] <- "-"
```



