---
title: "tree_test_leaflet"
output: html_document
date: '2023-02-19'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Map 2: Tree Regeneration By Size Class
Map 5: Regeneration Composition
Map 6: Canopy Composition
Map 8: Priority Invasive Composition
Map 8b: Not done by NETN, but agreed that we'd all like a map of relative abundance of Native versus Exotic by plot.  Should be very straigtforward, two colors (one for native, one for exotic)

```{r}
library(tidyverse) 
library(dplyr)
library(httr)
library(rgdal) 
library(sf) 
library(RColorBrewer)
library(sp) 
library(rgeos)
library(leaflet)
library(leaflet.minicharts)
library(mapview)
library(lubridate)

#testing more mapping for CUPN


#setwd("C:/Users/kseeger/OneDrive - DOI/Desktop/GIT_RSTUDIO/FlexdashboardPractice/Mapping/CUPN")
tree_basics <- read_csv(here::here("DataIn", "TreeBasics_20221013.csv"))
seed_sap <- read_csv(here::here("DataIn", "SeedlingSapling_20221013.csv"))
#seed_sap has become only CARL plots in this script

```

#Seedling and Sapling data for CUPN CARL Plots 
```{r}
seed_sap <- seed_sap %>%
dplyr::filter(Event_Type_Name != "QA/QC")

```

#CUPN Plot Lat and Long
```{r}
cupn_plots <- read_csv(here::here("DataIn", "CUPN_PlotEvents_LatLong.csv"))

cupn_plots_select <- cupn_plots %>%
    dplyr::select(Plot_Code, Start_Date, Latitude, Longitude)

cupn_plots_select$Start_Date <- dmy(cupn_plots_select$Start_Date)

cupn_plots_select <- cupn_plots_select %>%
  group_by(Plot_Code) %>%
  slice(which.max(Start_Date))

cupn_plots_select <- cupn_plots_select %>%
    dplyr::select(-Start_Date)

```

#adding CUPN shapefiles 
```{r}
cupn_boundary <- here::here('./cupnshapefile/CUPN.shp')

st_crs(cupn_boundary)

library(sf)

cupn_boundary <- st_transform(cupn_boundary, crs = 4326)

```

#creating color palettes
```{r}
okabe_ito <- c( "#0072B2", "#D55E00", 
               "#CC79A7", "#000000",  '#CC6677', '#BBCC33', '#99DDFF', 
                '#332288', '#882255', '#FFAABB', "#E69F00", "#56B4E9", "#009E73", "#F0E442")

viridis <- c("#fde725", "#5ec962", "#21918c","#3b528b","#440154")

```

#selecting top 13 species present in seedling/saplings and tree species
#TRY USING FORCATS() PACKAGE: FCT_LUMP()

```{r}
#Seedling Sapling

# trying code to see if fct_lump would be a better alternative
# lword <- seed_sap %>%
# filter(!is.na(Plant_Code)) %>%
# mutate(Plant_Code = fct_lump(Plant_Code, n = 10)) %>%
# count(Plant_Code)

top_species <- seed_sap %>%
dplyr::mutate(Plant_Code = as.factor(Plant_Code)) %>%
  dplyr::group_by(Plant_Code) %>%
  dplyr::summarise(Observations = n()) %>%
  dplyr::arrange(desc(Observations))  %>%
dplyr::mutate(Plant_Code = as.character(Plant_Code))

top_species <- as.data.frame(top_species[top_species$Observations >400,])

tree_basics_count <- tree_basics %>%
  dplyr::filter(Event_Type_Name != "QA/QC") %>%
dplyr::filter(Status_Code == 1) %>%
  dplyr::mutate(Basal_Area_ha = ((pi * DBH^2) /40000 )/0.04)

#Tree
top_tree <- tree_basics_count %>%
dplyr::mutate(Plant_Code = as.factor(Plant_Code)) %>%
  group_by(Plant_Code) %>%
  summarise(Observations = n()) %>%
  arrange(desc(Observations))  %>%
dplyr::mutate(Plant_Code = as.character(Plant_Code))

top_tree <- as.data.frame(top_tree[top_tree$Observations >400,])
```

#creating list of most frequently occuring tree species
```{r}

species_col_palette <- inner_join(top_tree, top_species, by = "Plant_Code")
  
#species_col_palette <- rbind(top_tree, top_species)

species_col_palette <- species_col_palette %>%
  dplyr::select(Plant_Code) %>%
  dplyr::mutate(Plant_Code = as.factor(Plant_Code))

species_col_palette <- unique(species_col_palette)

tree_count_test <- tree_basics_count %>%
dplyr::filter(Plant_Code %in% species_col_palette$Plant_Code)

unique(tree_count_test$Plant_Code)
```

#creating "Other category" in tree species count
```{r}
tree_basics_test_other <- tree_basics_count %>%
dplyr::filter(!Plant_Code %in% species_col_palette$Plant_Code)

tree_basics_test_other <- tree_basics_test_other %>%
  group_by(Plot_Code) %>%
  summarize(Other = n())
```

#creating tree_count: # basal area, # other, # obs per species
```{r}
#count number of observations of trees for tree density
tree_count_test <- tree_count_test %>%
  group_by(Plot_Code, Plant_Code) %>%
  summarize(DBH_Obs = n()) %>%
  ungroup()

tree_count_test <- tree_count_test %>%
  pivot_wider(names_from = Plant_Code, 
              values_from = DBH_Obs)

tree_count_test <- tree_count_test %>%
  select(Plot_Code, sort(tidyselect::peek_vars()))

tree_ba_test<- tree_basics_count %>%
  group_by(Plot_Code) %>%
  summarise(Sum = sum(Basal_Area_ha))

tree_plot_test <-  Reduce(function (...) { merge(..., all = TRUE) },  # Full join
                           list(tree_ba_test, tree_basics_test_other, tree_count_test, cupn_plots_select))

tree_plot_test <- tree_plot_test %>%
  filter(!is.na(Latitude)) %>%
  filter(!is.na(Longitude))
```


```{r, eval = FALSE}
inputpark <-"COWP"

#inputparl <- reactive$input

park_zoom <- tree_plot_test %>%
  dplyr::filter(grepl(inputpark, Plot_Code))

```

```{r}
      # fitBounds(min(tree_plot_test$Longitude), min(tree_plot_test$Latitude), max(tree_plot_test$Longitude), max(tree_plot_test$Latitude))
```

#mapping subsetted TREE data
```{r}
baseman_carl = leaflet(data = tree_plot_test) %>%
  addTiles() %>%
  #addProviderTiles("Esri.WorldImagery", options = providerTileOptions(noWrap = TRUE), group="Satellite") %>%
  addPolygons(data = cupn_boundary, color = ~ "black") %>%
  addCircleMarkers(tree_plot_test$Longitude,
                   tree_plot_test$Latitude,  color = ~ "black", weight = 1, fillColor = ~"blue", fillOpacity = 1, radius = 4)

#SET VIEW SETS THE MIDDLE POINT OF THE MAP BUT DOES NOT NECESARRILY HELP FOR VIEWING PURPOSES
#  setView(lng = mean(tree_plot_test$Longitude), lat = mean(tree_plot_test$Latitude), zoom = 15)

baseman_carl <- baseman_carl %>%
  addMinicharts(tree_plot_test$Longitude, 
                tree_plot_test$Latitude, 
    chartdata =dplyr::select(tree_plot_test, -c(Plot_Code, Latitude, Longitude)), 
    type = "pie",
    width = sqrt(tree_plot_test$Sum) * 4,
    col = okabe_ito,
    showLabels = F) %>%
  addLabelOnlyMarkers(tree_plot_test$Longitude, 
                tree_plot_test$Latitude, label =  tree_plot_test$Plot_Code,
                      labelOptions = labelOptions(noHide = T, direction = 'top', textOnly = T, style=list('color'="#ffffff", 'fontSize'="15px"))) %>%
  fitBounds(min(park_zoom$Longitude), min(park_zoom$Latitude), max(park_zoom$Longitude), max(park_zoom$Latitude))


baseman_carl
#mapshot(baseman_carl, file = "Map_TreeCanopy_Comp.png")
```
