---
title: "VegConstancy"
output: html_document
date: '2022-11-22'
---
```{r}
knitr::opts_chunk$set(echo = FALSE)

library(tidyr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(readr)
library(knitr)
library(base)
library(stringr)
library(gt)
library(psych)
library(reactable)
library(sparkline)

#these GENERAL Viz RMDs are to create a flexdashboard compatible/generalized for all networks

```

```{r}
#Set Working Directory
#setwd("C:/Users/kseeger/OneDrive - DOI/Desktop/GIT_RSTUDIO/FlexdashboardPractice")
constancy <- read_csv(here::here("DataIn", "Constancy_Data.csv"))
constancy_full <- read_csv(here::here("DataIn", "Constancy_Data_Full.csv"))
```

#ORIGINAL CODE COVER CALC
```{r}
#Finding Average Mean Plot Cover by Species across broad habitat types
cover_calc <- constancy_full %>%
  dplyr::select(`BROAD HABITAT TYPE`, 
                Species_Original,
                `Mean Plot Cover`) %>%
  group_by(`BROAD HABITAT TYPE`,
           Species_Original) %>%
  summarise(Avg_MPC = mean(`Mean Plot Cover`))%>%
  ungroup()

#Pivoting
cover_calc <- cover_calc %>%
  pivot_wider(
    names_from = `BROAD HABITAT TYPE`, 
    values_from = Avg_MPC
  )

cover_calc <- cover_calc %>%
  rename(CPNW = `Coastal Plain Nonalluvial Wetlands`, 
         CPOUW = `Coastal Plain Open Uplands and Woodlands`, 
         MUFS = `Maritime Upland Forests and Shrublands`)

```

#GENERAL CODE COVER CALC
#BIG CAVEAT IS THAT PLANT_CODE COULD ALSO BE SPECIES_DIVERSITY_ID and GROUP COULD BE SOME OTHER GROUPING COLUMN NAME
```{r}
#Finding Average Mean Plot Cover by Species across broad habitat types
cover_calc <- constancy_full %>%
  dplyr::select(`GROUP`, 
                Plant_Code,
                `Mean Plot Cover`) %>%
  group_by(`GROUP`,
           Plant_Code) %>%
  summarise(Avg_MPC = mean(`Mean Plot Cover`)) %>%
  ungroup()
```
# ^ using original code to create cover_calc variable before "GROUP" column comes into existence 
```{r}
makeInitials <- function(charVec) {
  make.unique(vapply(strsplit(toupper(charVec), " "), 
                     function(x) paste(substr(x, 1, 1), collapse = ""), 
                     vector("character", 1L)))
}

#Creating function to get acronyms from "grouped" column
cover_calc <- cover_calc %>%
  mutate(Group = mapply(function(charVec) makeInitials(charVec), `BROAD HABITAT TYPE`)) #BHT = `GROUP`
  

#Pivoting
cover_calc <- cover_calc %>%
  select(Species_Original, Group, Avg_MPC) %>%
    pivot_wider(names_from = `Group`, 
    values_from = Avg_MPC
  )

cover_calc

```

#ORIGINAL CODE COVER CODE
```{r}
#Calculating Cover Code
#Is it worth it to figure out for loops???

cover_code <- cover_calc %>%
  dplyr::mutate(CPNW_Cover = case_when(
    CPNW == NA ~ "",
    CPNW >= 0 & CPNW <=0.1~ "1", 
    CPNW >= 0.1 & CPNW <=1~ "2",
    CPNW >= 1 & CPNW <= 2 ~ "3",
    CPNW >= 2 & CPNW <= 5 ~ "4",
    CPNW >= 5 & CPNW <= 10 ~ "5",
    CPNW >= 10 & CPNW <=25~ "6",
    CPNW >= 25 & CPNW <=50~ "7",
    CPNW >= 50 & CPNW <= 75 ~ "8",
    CPNW >= 75 & CPNW <=95 ~ "9",
    CPNW >= 95 & CPNW <= 100 ~ "10"),
CPOUW_Cover = case_when(CPOUW == NA ~ "",
    CPOUW >= 0 & CPOUW <=0.1~ "1", 
    CPOUW >= 0.1 & CPOUW <=1~ "2",
    CPOUW >= 1 & CPOUW <= 2 ~ "3",
    CPOUW >= 2 & CPOUW <= 5 ~ "4",
    CPOUW >= 5 & CPOUW <= 10 ~ "5",
    CPOUW >= 10 & CPOUW <=25~ "6",
    CPOUW >= 25 & CPOUW <=50~ "7",
    CPOUW >= 50 & CPOUW <= 75 ~ "8",
    CPOUW >= 75 & CPOUW <=95 ~ "9",
    CPOUW >= 95 & CPOUW <= 100 ~ "10"),
MUFS_Cover = case_when(MUFS == NA ~ "",
                     MUFS >= 0 & MUFS <=0.1~ "1",
                     MUFS >= 0.1 & MUFS <=1~ "2",
                     MUFS >= 1 & MUFS <= 2 ~ "3",
                     MUFS >= 2 & MUFS <= 5 ~ "4",
                     MUFS >= 5 & MUFS <= 10 ~ "5",
                     MUFS >= 10 & MUFS <=25~ "6",
                     MUFS >= 25 & MUFS <=50~ "7",
                     MUFS >= 50 & MUFS <= 75 ~ "8",
                     MUFS >= 75 & MUFS <=95 ~ "9",
                     MUFS >= 95 & MUFS <= 100 ~ "10")
    
  )
```
#ORIGINAL CODE ""
```{r}
#Cover Calculations 
cover_code <- cover_code %>%
  dplyr::mutate(CPNW_Cover = as.numeric(CPNW_Cover), 
         CPOUW_Cover = as.numeric(CPOUW_Cover), 
         MUFS_Cover = as.numeric(MUFS_Cover))
```

#GENERAL CODE COVER CODE
```{r}

cover_calc %>%
  mutate_if(is.numeric, list(~case_when(. >= 0 & . <= 0.1 ~ "1")))


cover_code <- cover_calc %>%
  mutate_if(is.numeric, list(~case_when(
    . >= 0 & . <=0.1~ "1",
                     . >= 0.1 & . <=1~ "2",
                     . >= 1 & . <= 2 ~ "3",
                     . >= 2 & . <= 5 ~ "4",
                     . >= 5 & . <= 10 ~ "5",
                     . >= 10 & . <=25~ "6",
                     . >= 25 & . <=50~ "7",
                     . >= 50 & . <= 75 ~ "8",
                     . >= 75 & . <=95 ~ "9",
                     . >= 95 & . <= 100 ~ "10" )
  ))

cover_code <- cover_code %>%
 # select(-Species_Original) %>% #general code would be -Plant_Code
  rename_at(vars(-Species_Original),function(x) paste0(x,"_Cover")) %>%
  mutate_at(vars(-Species_Original), as.integer)
```

#ORIGINAL CODE CONSTANCY COUNT
```{r}
#Finding count of "event_name_date_calc" /species? across broad habitat types 

constancy_count <- constancy_full %>%
  dplyr::select(`BROAD HABITAT TYPE`, Species_Original, `Mean Plot Cover`) %>%
  group_by(`BROAD HABITAT TYPE`, Species_Original) %>%
  summarise(Species_Total = n()) 

constancy_count <- constancy_count %>%
  pivot_wider(
    names_from = `BROAD HABITAT TYPE`, 
    values_from = Species_Total
  )

```

#GENERAL CODE CONSTANCY COUNT 
```{r}
#Finding count of "event_name_date_calc" /species? across broad habitat types 

constancy_count <- constancy_full %>%
  dplyr::select(`GROUP`, Plant_Code, `Mean Plot Cover`) %>%
  group_by(`GROUP`, Plant_Code) %>%
  summarise(Species_Total = n()) 

constancy_count <- constancy_count %>%
  pivot_wider(
    names_from = `GROUP`, 
    values_from = Species_Total
  )

```

#ORIGINAL CODE FOR FINDING CONSTANCY COUNT 
```{r}
#Calculating Constancy values 
constancy_count <- constancy_count %>%
  replace(is.na(.), 0) %>%
  dplyr::mutate(
    CPNW_Constancy = ((`Coastal Plain Nonalluvial Wetlands`/max(`Coastal Plain Nonalluvial Wetlands`)) * 100),
    CPOUW_Constancy = ((`Coastal Plain Open Uplands and Woodlands`/max(`Coastal Plain Open Uplands and Woodlands`)) * 100), 
    MUFS_Constancy = ((`Maritime Upland Forests and Shrublands`/max(`Maritime Upland Forests and Shrublands`))*100 )
  )
```
#ORIGINAL CODE CONTD
```{r}
constancy_plot_num <- constancy_full%>%
  group_by(`BROAD HABITAT TYPE`, event_name_date_calc) %>%
  summarize(n()) %>%
  ungroup() %>%
  group_by(`BROAD HABITAT TYPE`) %>%
  summarize(Num_Plots = n()) 

constancy_count <- constancy_full %>%
  dplyr::select(`BROAD HABITAT TYPE`, Species_Original, `Mean Plot Cover`) %>%
  group_by(`BROAD HABITAT TYPE`, Species_Original) %>%
  summarise(Species_Total = n())
  

constancy_count <- left_join(constancy_count, constancy_plot_num, by = "BROAD HABITAT TYPE")

constancy_count <- constancy_count %>% 
  dplyr::group_by(`BROAD HABITAT TYPE`) %>%
  dplyr::mutate(Constancy = (Species_Total/Num_Plots)) %>%
  dplyr::select(`BROAD HABITAT TYPE`, Species_Original, Constancy) %>%
  ungroup()

constancy_count <- constancy_count %>%
   mutate(Group = mapply(function(charVec) makeInitials(charVec), `BROAD HABITAT TYPE`)) #BHT = `GROUP`

constancy_count <- constancy_count %>%
  select(-`BROAD HABITAT TYPE`) %>%
  pivot_wider(names_from = Group, 
              values_from = Constancy)

constancy_count <- constancy_count %>%
    rename_at(vars(-Species_Original),function(x) paste0(x,"_Constancy")) 

```



#GENERAL CODE/MORE SUSTAINABLE CODE FOR CALCULATING CONSTANCY COUNT
```{r}
constancy_plot_num <- constancy_full%>%
  group_by(`GROUP`, event_name_date_calc) %>% #UNSURE IS EVENT_NAME_DATE_CALC IS A UNIVERSAL VARIABLE
  summarize(n()) %>%
  ungroup() %>%
  group_by(`GROUP`) %>%
  summarize(Num_Plots = n())


constancy_count <- constancy_full %>%
  dplyr::select(`GROUP`, Plant_Code, `Mean Plot Cover`) %>%
  group_by(`GROUP`, Plant_Code) %>%
  summarise(Species_Total = n()) 

constancy_count <- left_join(constancy_count, constancy_plot_num, by = "GROUP")


constancy_count <- constancy_count %>% 
  dplyr::group_by(`GROUP`) %>%
  dplyr::mutate(Constancy = (Species_Total/Num_Plots)) %>%
  dplyr::select(`GROUP`, Species_Original, Constancy) %>%
  ungroup()

constancy_count <- constancy_count %>%
   mutate(Group = mapply(function(charVec) makeInitials(charVec), `GROUP`)) #BHT = `GROUP`

constancy_count <- constancy_count %>%
  select(-`GROUP`) %>%
  pivot_wider(names_from = Group, 
              values_from = Constancy)

constancy_count <- constancy_count %>%
    rename_at(vars(-Species_Original),function(x) paste0(x,"_Constancy"))
```


#ROUNDING FUNCTION
```{r}
round_df <- function(x, digits) {
    numeric_columns <- sapply(x, mode) == 'numeric'
    x[numeric_columns] <-  round(x[numeric_columns], digits)
    x
}

constancy_count <- round_df(constancy_count, 0)

```

#ORIGINAL CODE FOR CREATING SUBSETTED DATASETS TO MERGE TOGETHER
```{r}
cover_calc_code <- cover_code %>%
  dplyr::select(Species_Original, CPNW_Cover, CPOUW_Cover, MUFS_Cover) 

constancy_count_code <- constancy_count %>%
  dplyr::select(Species_Original, CPNW_Constancy, CPOUW_Constancy, MUFS_Constancy) 
```

#GENERAL CODE FOR CREATING SUBSETTED DATASETS TO MERGE TOGETHER
```{r}
#not needed! 
```

#ORIGINAL CODE FOR CREATING FINAL DATASET
```{r}
constancy_final <- Reduce(function (...) { merge(..., all = TRUE) },  # Full join
                           list(cover_calc_code, constancy_count_code))
```

```{r}
constancy_final <- constancy_final %>%
  dplyr::select(Species_Original, CPNW_Constancy, CPNW_Cover, CPOUW_Constancy, CPOUW_Cover, MUFS_Constancy, MUFS_Cover)
```

```{r}
constancy_final[constancy_final == 0] <- NA

constancy_final[is.na(constancy_final)] <- "-"

constancy_final
```

#GENERAL CODE FOR CREATING FINAL DATASET
```{r}
constancy_final <- Reduce(function (...) { merge(..., all = TRUE) },  #full join idk why I can't just do a regular left join....
                        list(cover_calc_cover, constancy_count_code))
```

```{r}
constancy_final[constancy_final == 0] <- NA

constancy_final[is.na(constancy_final)] <- "-"

constancy_final<- constancy_final  %>%
  tidyr::pivot_longer(cols = - Species_Original,
               names_to = "codes", 
               values_to = "value") %>%
  dplyr::arrange(codes) %>%
  tidyr::pivot_wider(names_from = "codes", 
              values_from = "value")
```
 
